---
title: 'Paving the Way: Women as Mentors and Advocates for Junior Statisticians'
author: "Jessica Minnier, PhD<br><span style = 'font-size: 50%;'>Associate Professor of Biostatistics<br>OHSU-PSU School of Public Health<br>Knight Cancer Institute Biostatistics Shared Resource<br>Oregon Health & Science University</span>"
date: 'WNAR 2021<br><br>`r icon::fa("link")` [bit.ly/wnar-fn](https://bit.ly/wnar-fn)<br>`r icon::fa("twitter")` [datapointier](https://twitter.com/datapointier)'
output:
  xaringan::moon_reader:
    css: [css/xaringan-themer.css, css/my-theme.css]
    lib_dir: libs
    nature:
      countIncrementalSlides: false
      titleSlideClass: ["left", "middle", "inverse"]
      highlightLines: true
      highlightStyle: solarized-dark
      ratio: "16:9"
    includes:
      in_header: ../libs/header.html
---

layout: true


---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

library(tidyverse)

knitr::opts_chunk$set(
  warning=FALSE, 
  message=FALSE, 
  fig.width=10.5, 
  fig.height=4, 
  comment=NA, 
  rows.print=16,
  echo=FALSE)
theme_set(theme_bw(base_size = 24))

library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "alphabetic",
           style = "markdown",
           hyperlink = FALSE,
           dashed = FALSE)
myBib <- ReadBib("./minnier_bibliography.bib", check = FALSE)
#Citet(myBib, key="peng2011reproducible")
#citeNatbib(key="peng2011reproducible", bib=myBib, textual = TRUE)
```

```{r xaringan-themer, include = FALSE}
# creates xaringan theme
# devtools::install_github("gadenbuie/xaringanthemer")
library(xaringanthemer)
mono_light(
  base_color =  "#3A6185", ## OHSU Marquam
  code_highlight_color = "#cbdded",
  link_color = "#38BDDE",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i","400i","700"),
  code_font_google   = NULL,
  text_font_size = "22px",
  code_font_size = "18px",
  header_h1_font_size = "45px",
  header_h2_font_size = "40px",
  header_h3_font_size = "35px",
  padding = "0em 2em 1em 2em",
  outfile = "css/xaringan-themer.css"
)
```

# Introduction and Inspiration

## Florence Nightingale (1820-1910)

- In 1840, FN begged her parents to study mathematics
- Mother: "did not approve, home duties were not to be neglected for mathematics"
- Father, loved math, but encouraged study of other subjects (history or philosophy)
- Eventually, was allowed to have tutors in mathematics (arithmetic, geometry, aglebra), and later tutored children in these subjects and showed concern about education of girls in math

[Florence Nightingale, Amstat Magazine 22-Sept-2016](https://magazine.amstat.org/blog/2016/09/22/sih-nightingale/%E2%80%8E)


???

Hello everyone, today I wanted to talk about mentoring. We are inspired by Florence Nightingale's work in empowering women in nursing and statistics. 

---

# Note

- Cautioned against extremism, “which urges women to do all that men do...merely because men do it, and without regard to whether this is the best that women can do.”

[Florence Nightingale, Amstat Magazine 22-Sept-2016](https://magazine.amstat.org/blog/2016/09/22/sih-nightingale/%E2%80%8E)

??
I will say this is not without controversy, because although Florence Nightingale spoke out in favor of
she seemed to still harbor some biases, and did not hire women into high paying medical jobs.

