---
title: "Sharpening the Tools in Your Data Science Toolbox"
author: "Jessica Minnier, PhD<br><span style = 'font-size: 50%;'>OHSU-PSU School of Public Health<br>Knight Cancer Institute Biostatistics Shared Resource<br>Oregon Health & Science University</span>"
date: '[Joint Statistical Meetings](https://ww2.amstat.org/meetings/jsm/2019/onlineprogram/ActivityDetails.cfm?sessionid=218337), July 29, 2019<br><br>`r icon::fa("link")` [bit.ly/jmin-jsm19](https://bit.ly/jmin-jsm19)<br>`r icon::fa("twitter")` [datapointier](https://twitter.com/datapointier)'
output:
  xaringan::moon_reader:
    css: [xaringan-themer.css, libs/my-theme-nologo.css]
    lib_dir: libs
    nature:
      countIncrementalSlides: false
      titleSlideClass: ["left", "middle", "inverse"]
      highlightLines: true
      highlightStyle: solarized-dark
      ratio: "16:9"
    includes:
      in_header: ../libs/header.html
---

layout: true
  
<div class="my-footer"><span>bit.ly/jmin-jsm19</span></div> 


---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)

library(tidyverse)

knitr::opts_chunk$set(
  warning=FALSE, 
  message=FALSE, 
  fig.width=10.5, 
  fig.height=4, 
  comment=NA, 
  rows.print=16,
  echo=FALSE)
theme_set(theme_bw(base_size = 24))
```


```{r xaringan-themer, include = FALSE}
# devtools::install_github("gadenbuie/xaringanthemer")
library(xaringanthemer)
mono_light(
  base_color =  "#3A6185", #5e97c9" ## OHSU Marquam, #"#125972" ## picked to coordinate with rOpenSci logo 
  code_highlight_color = "#c0e8f5",
  link_color = "#38BDDE",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Droid Mono"),
  text_font_size = "26px"
)
```

class: inverse, center, middle

[DRAFT SLIDES]

---

# Outline

---

# Statistics is changing


[How does data science differ from statistics? Is it the same? Many different opinions,
depends on industry/career]

---

# Programming has definitely changed

- Data Science is programming intensive
  + Big data and complex models (machine learning)
- Beyond SAS
  + R is easier to learn than ever before (see: tidyverse)
  + R packages are easier to make
  + R is not "slow" anymore
- Python is most common in data science
  + but not statistics!

---

# Improve your coding skills

[Online resources/courses]

---

# Coding in R is more fun

- knitr $\to$ reproducible documents
  + these slides are made with knitr/r markdown
  + make textbooks, webpages, much more
- Shiny $\to$ webpages to show off methodology/analyses

---

# Software Development

- Unix/shell
- Programming
- Version control (git/github/gitlab, bitbucket)
- Unit Testing (does your code work?)
- Collaborative coding
- Using databases (SQL)
- Automation (make)

---


# How to learn software development?

- Software Carpentries (2 day intensive workshops)


---

# Learn together

- Hackweeks 
- Data Science Workshops
- Data competitions (DataFest)
- Workshops at conferences (SDSS, Rstudio::conf, local R conferences)

---

# Find a community

We all have something to learn!

[R conferences, meetup groups, students or employees who are also learning, twitter]

---

# Practice, practice, practice

- Learning a tool and then forgetting to use it is the best way to unlearn it

---

# Give talks

- Sign up to give talks at local meetups
- Teach workshops to students/fellow faculty/coworkers

---

# We don't want to be left behind

- Work on projects outside of your comfort zone
- Grow as statisticians, grow as a field
- Be open to other fields collaborating on "data science"

---

# Thank you!


Contact me: `r icon::fa("envelope")` minnier-[at]-ohsu.edu, `r icon::fa("twitter")` [datapointier](https://twitter.com/datapointier), `r icon::fa("github")` [jminnier](https://github.com/jminnier/)

Slides available: [bit.ly/jmin-jsm19](https://bit.ly/jmin-jsm19)

Slide code available at: [github.com/jminnier/talks-etc](https://github.com/jminnier/talks_etc)
